Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
minor change

The goal of our experiment was to retrieve all the bugs that FindBugs reports,
from all the project versions existing on the Maven repository.
The experiment involved four entities:
a number of {\it workers} (a custom Python script), a {\it task queue}
mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was
the public Maven repository.

@@

FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
Malicious Code}. From the total number of versions, 4,353 of them contained
at least one bug coming from the first category
and 45,559 coming from the second.

>>>>

The goal of our experiment was to retrieve all the bugs that FindBugs reports,
from all the project versions existing on the Maven repository (in the Maven
repository, versions are {\it actual} releases). The experiment involved four entities:
a number of {\it workers} (a custom Python script), a {\it task queue}
mechanism (Rabbit{\sc mq} - version 3.0.1),\footnote{\url{http://www.rabbitmq.com/}}
a {\it data repository} (Mongo{\sc db} - version 2.2),\footnote{\url{http://www.mongodb.org/}}
and the {\it code repository}, which in our case it was
the public Maven repository.

@@

FindBugs separates software bugs into nine categories (see
Table~\ref{tbl:bug-cat}). Two of them involve security issues: {\it Security} and {\it
Malicious Code}. From the total number of releases, 4,353 of them contained
at least one bug coming from the first category
and 45,559 coming from the second.
